Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{{DISTRIBUTION STATEMENT A. Approved for public release.} }

### 2021-05-15 paper/case-study.tex
Wordsmithing in the Case Study section

We have modeled the system architecture of the UAV in AADL.  It includes a Mission Computer for communicating with the ground station and generating flight plans, and a Flight Control Computer for UAV navigation.  The Mission Computer architecture model includes hardware components such as a processor, memory, and communication devices, as well as software.
%
The initial software architecture model (shown in \figref{fig:sw-initial}) contains drivers for communication with the Ground Station and Flight Control Computer, a Waypoint Manager component that provides flight plan coordinates to the Flight Control Computer, and the Flight Planner.  The Flight Planner is the open-source UxAS software developed by AFRL~\cite{uxas}.

@@

The filter behavior for each component is specified in AGREE.  Not only does this enable formal verification within the modeling environment, but it also provides a means for synthesizing the component implementation in a provably correct manner using the SPLAT tool.  Because SPLAT is integrated with BriefCASE, the proof it emits when synthesizing component code is used as evidence in the Resolute goal for the corresponding mitigation.  When Resolute evaluates whether such a goal is supported by evidence, it checks for the existence of the synthesis proof in addition to verifying the architecture is correct.

The AGREE filter policies for the four UxAS connections are similar, and check that record values contained in the messages are within appropriate ranges.  For example, the Automation Response message filter, which drops messages containing malformed flight plans, is defined as shown in \figref{fig:automation-response-filter}.  Although \texttt{Latitude}, \texttt{Longitude} and \texttt{Altitude} are defined as 64-bit \textit{reals}, the filter only passes messages containing waypoint values between [-90,90], [-180,180], and [0,15000], respectively.

@@

Once we have determined that the model is correct and satisfies its cyber requirements, and the software components in the model have been implemented, either by SPLAT or other means, the system can be built and deployed.  We run the HAMR tool to generate the component stubs and infrastructure code necessary to enable component communication and execution according to a specified schedule.
HAMR translates the AADL system model to code that implements threading infrastructure and inter-component communication and is consistent with the AADL specification computational model.
%
HAMR then compiles the software to execute on seL4~\cite{sel4-2009}, a verified capability-based microkernel (accompanied by formal proof of spatial isolation properties down to the binary level).

@@

We first performed a set of tests on the initial system (\figref{fig:sw-initial}) prior to applying our cyber-resiliency mitigations in order to verify the effectiveness of the malicious code.  
We repeated the tests on the hardened system and were able to demonstrate that our mitigations were successful.
The following scenarios were exercised (status messages from the high-assurance components in the hardened system are shown in \figref{fig:mitigation-output}):

@@

\paragraph{UxAS trojan modifies flight plan} In this scenario, a trojan embedded in UxAS will attempt to cause the UAV to fly into the specified keep-out zone by modifying the mission command waypoints in the Automation Response.  
On the hardened system the Geofence Monitor detected that it was being instructed to fly into a keep-out zone and instead returned the UAV to Home Base.

>>>>

We have modeled the system architecture of the UAV in AADL.  The model includes a Mission Computer for communicating with the ground station and generating flight plans, and a Flight Control Computer for UAV navigation.  The Mission Computer architecture model includes hardware components such as a processor, memory, and communication devices, as well as software.
%
The initial software architecture model (shown in \figref{fig:sw-initial}) contains drivers for communication with the Ground Station and Flight Control Computer, a Waypoint Manager component that provides flight plan coordinates to the Flight Control Computer, and the Flight Planner.  The Flight Planner is the open-source UxAS software developed by AFRL~\cite{uxas}.

@@

The filter behavior for each component is specified in AGREE.  Not only does this enable formal verification within the modeling environment, but it also provides a means for synthesizing the component implementation in a provably correct manner using the SPLAT tool.  Because SPLAT is integrated with BriefCASE, the proof it emits when synthesizing component code is used as evidence in the Resolute goal for the corresponding mitigation.  When Resolute evaluates whether such a goal is supported by evidence, it checks for the existence of the synthesis proof in addition to verifying that the architecture is correct.

The AGREE filter policies for the four UxAS connections are similar, and check that record values contained in the messages are within appropriate ranges.  For example, the Automation Response message filter, which drops messages containing malformed flight plans, is defined as shown in \figref{fig:automation-response-filter}.  Although \texttt{Latitude}, \texttt{Longitude} and \texttt{Altitude} are defined as 64-bit floating-point values, the filter only passes messages containing waypoint values between [-90,90], [-180,180], and [0,15000], respectively.

@@

Once we have determined that the model is correct and satisfies its cyber requirements, and the software components in the model have been implemented, either by SPLAT or other means, the system can be built and deployed.  We run the HAMR tool to generate the component stubs and infrastructure code necessary to enable component communication and execution according to a specified schedule.
HAMR translates the AADL system model to code that implements threading infrastructure and inter-component communication consistent with the AADL computational model.
%
HAMR then compiles the software to execute on seL4~\cite{sel4-2009}, a verified capability-based microkernel (accompanied by formal proof of spatial isolation properties down to the binary level).

@@

We first performed a set of tests on the initial system (\figref{fig:sw-initial}) prior to applying our cyber-resiliency mitigations in order to verify the effectiveness of the malicious code.  
A third party evaluator repeated the tests on the hardened system and were able to demonstrate that our mitigations were successful.
The following scenarios were exercised (status messages from the high-assurance components in the hardened system are shown in \figref{fig:mitigation-output}):

@@

\paragraph{UxAS trojan modifies flight plan} In this scenario, a trojan embedded in UxAS attempts to cause the UAV to fly into the specified keep-out zone by modifying the mission command waypoints in the Automation Response.  
On the hardened system the Geofence Monitor detected that it was being instructed to fly into a keep-out zone and instead returned the UAV to Home Base.
